Study of Intra/Inter-Application Interference for Smart Job Allocation on HPC system

### 2015-09-20 submission.tex
redraw and update figs

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Smart HPC Job Allocation with Communication Pattern Awareness}
% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{

@@

In this work, we provide detailed analysis about the communication pattern of two DOE MiniApps. MiniApps are reduced proxy applications that encapsulate the salient performance of larger full size applications\cite{miniapp}. Since we only focus on the dominant communication pattern of parallel applications, these MiniApps are perfect candidates for analysis the application's performance on different allocations or on new network architectures.

@@

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/appstudy/amg/amg_ct}
   \caption{Communication Topology of AMG with 27 MPI Ranks }
   \label{fig: amg communication topology}
\end{figure}

@@

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/appstudy/cr/cr10_ct}
   \caption{Communication Topology of Crystal Router with 10 MPI Ranks }
   \label{fig: crystalrouter10 communication topology}
\end{figure}

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/appstudy/cr/cr100_ct}
   \caption{Communication Topology of Crystal Router with 100 MPI Ranks }
   \label{fig: crystalrouter100 communication topology}
\end{figure}

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/appstudy/cr/cr_data_transfer}
   \caption{The amount of data each rank transferred in Crystal Router. }
   \label{fig: cr data trans}
\end{figure}

@@

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/appstudy/mg/mg125_ct}
   \caption{Communication Topology of MultiGrid with 125 MPI Ranks }
   \label{fig: multigrid125 communication topology}
\end{figure}

@@

\section{Simulation Platform}
\label{sec:simulation}

@@

\section{Communication Pattern Aware Allocation Policy }
In this section, we will explore the performance of three applications on different allocations in a 3D torus network. First, we analysis the impact from different allocation shape, then we will present the results by using our communication aware allocation policy.

@@

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Study of Intra/Inter-Application Interference for Smart Job Allocation on HPC system}
% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{

@@

In this work, we provide detailed analysis about the communication pattern of two DOE MiniApps. MiniApps are reduced proxy applications that encapsulate the salient performance of larger full size applications\cite{miniapp}. Since we only focus on the dominant communication pattern of parallel applications, these MiniApps are perfect candidates for analysis the application's performance on different allocations or on new network architectures. We choose three MiniApps, namely, Algebraic Multigrid Solver(AMG), Geometric MultiGrid(MultiGrid) and CrystalRouter. Their communication patterns can be representative for most MiniApps listed on the DOE Design Forward Webpage\cite{design forward webpage}. The communication pattern figures we present here are generated with the IPM\cite{ipm} data from \cite{design forward webpage}.

@@

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/appstudy/amg/amg_ct}
   \caption{Rank-Rank communication topology of AMG with 27 mpi ranks. This figure is redrawed by collected data from\cite{design forward webpage}.   }
   \label{fig: amg communication topology}
\end{figure}

@@

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/appstudy/cr/cr10_ct}
   \caption{Rank-Rank communication topology of CrystalRouter with 10 mpi ranks. This figure is redrawed by collected data from\cite{design forward webpage}. }
   \label{fig: crystalrouter10 communication topology}
\end{figure}

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/appstudy/cr/cr100_ct}
   \caption{Rank-Rank communication topology of CrystalRouter with 100 mpi ranks. This figure is redrawed by collected data from\cite{design forward webpage}. }
   \label{fig: crystalrouter100 communication topology}
\end{figure}

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/appstudy/cr/cr_data_transfer}
   \caption{The amount of data each rank transferred in CrystalRouter. }
   \label{fig: cr data trans}
\end{figure}

@@

\begin{figure}[h!] 
  \centering
  \includegraphics[width=0.38\textwidth]{figs/appstudy/mg/mg125_ct}
   \caption{Rank-Rank communication topology of MultiGrid with 125 mpi ranks. This figure is redrawed by collected data from\cite{design forward webpage}. }
   \label{fig: multigrid125 communication topology}
\end{figure}

@@

\section{Research Vehicle}
\label{sec:simulation}

@@

\section{Interference Analysis}
In this section, we will explore the performance of three applications on different allocations in a 3D torus network. First, we analysis the impact from different allocation shape, then we will present the results by using our communication aware allocation policy.

@@

\bibitem{ipm}
David Skinner, Nicholas Wright, Karl Fuerlinger and Kathy Yelick
\newblock Integrated Performance Montoring(IPM)
\newblock Available http://ipm-hpc.sourceforge.net/overview.html
\newblock (Accessed on: Sept 16th. 2015)
